---
title: "生物信息导论"
author: "Songpeng Zu"
date: "Tuesday, October 07, 2014"
output:
  beamer_presentation:
    toc: true  
    keep_tex: true
---

# Intro 2 R
## Content
- R Basic    
  1.Install R and Rstudio  
  2.R classes  
  3.R statements  
  4.R functions and libraries    
  5.**R I/O**
- R graph  
  1.Basic graph  
  2.ggplot  
  3.**lattice**  
- **Others**  
  1.**Latex vs R markdown**    
  2.**Rcpp**  
  3.**R shiny**   
  4.**R regular expression**
  

## R Basic
- Install R  
<http://www.r-project.org/>  
- Rstudio is a powerful IDE for R.  
<http://www.rstudio.com/>  
- Working directory  
```{r,eval=FALSE}
getwd()
setwd("D:/")
```
## R classes  
character, numeric, integer, logical, **vector, matrix, factor, data frame, list.**  

- vector  
```{r,eval=FALSE}
x <- c(10,3,2,1,NA); x[4]; mode(x); length(x) 
```

- matrix
```{r,collapse=TRUE}
X <- matrix(1:12,nrow=3,byrow=TRUE,dimnames=NULL);X[1,]
rbind(X,c(3,2,1,3))
apply(X,2,mean)
```

## R classes
- factor: a compact way to handle categorical data.
```{r,collapse=TRUE}
sex <- c("M","F","M","F","F")
sex.factor <- as.factor(sex);table(sex.factor)
height <- c(174,165,180,171,160)
tapply(height,sex.factor,mean)
gl(2,3)
```
## R classes
- list: a useful way to combine a collection of different objects.
```{r,collapse=TRUE}
family <- list(name="Fred",wife="Jane",
               children=c("XY","XX"))
family$name;family[[3]][2];family[["wife"]]
family[1:2]
unlist(family)
```
## R classes
- data frame: a specific list of vectors and/or factors of the same length.
```{r,collapse=TRUE}
 df<-data.frame(
Name=c("Alice", "Becka", "James", "Jeffrey", "John"),
Sex=c("F", "F", "M", "M", "M"),
Age=c(13, 13, 12, 13, 12),
Height=c(56.5, 65.3, 57.3, 62.5, 59.0),
Weight=c(84.0, 98.0, 83.0, 84.0, 99.5)
); df
```
## R statements
```{r,eval=FALSE}
if(cond){expr}
else if(cond){expr}
else{expr}

for(var in seq){expr}

while(cond){expr}

break;next;
repeat {expr}
```
```{r,collapse=TRUE}
switch(3,1,2,3,4)
switch("mean",mean=mean(c(1,3,2)),median=3)
```
## R functions and libraries

```{r,eval=FALSE}
install.packages(packname)
library(packname)

funname <- function(arg1,arg2,...){
  statements
  return(objects)
}
```

```{r,collapse=TRUE}
centre <- function(x, type){
  switch(type,
         mean = mean(x),
         median = median(x))
}
x <- rcauchy(10)
centre(x, "mean")
```

## Basic graph
```{r,fig.height=5,fig.width=5,collapse=TRUE,warning=FALSE}
# Basic Scatterplot Matrix
pairs(~mpg+disp+drat+wt,data=mtcars)
```

## Basic graph
```{r,collapse=TRUE,warning=FALSE}
boxplot(len~supp*dose, data=ToothGrowth, notch=FALSE, 
  col=(c("gold","darkgreen")))
```

## ggplot
```{r,warning=FALSE,fig.height=3,fig.width=5,collapse=TRUE}
library(ggplot2)
qplot(wt, mpg, data=mtcars, geom=c("point", "smooth"), 
   method="lm", formula=y~x, color=cyl)
```

# Intro 2 Stats.
## Content
- Bayesian Stats  
  1.the Bayes Rule  
  2.prior   
  3.Hierachical Bayes   
- Frequentist Stats  
  1.Large sample theory for the MLE  
  2.p-value, FDR   

## Bayesian Stats
- Bayes Rule
$$Pr(\theta|Data) \varpropto Pr(\theta)Pr(Data|\theta)$$
- prior     
  1. Conjugate prior distribution  
  2. Jeffreys prior  
- Hierachical Bayes and an example.

## Frequentist Stats
- Large sample theory for the MLE  
- p-value  
- FDR  

## Reference  
- Peter Dalgaard, _Introductory Statistics with R_ 
- Winston Wang, _R Graphics Cookbook_
- <http://www.statmethods.net/>  
- Kevin P.Murphy, _Machine Learning: A Probabilistic Perspective_  
